### 2015-05-23 docs/report/function_transfer_time.tex

This can be achived by taking advantage of the global context object (detailed in Section~\ref{sec:context}).

@@

\note{The improvement will vary if the difference in character length between the key and the function's code does.}

>>>>

This can be achieved by taking advantage of the global context object (detailed in Section~\ref{sec:context}).

@@

The following listing shows the code for the benchmark:
\bmcode{http://jsperf.com/global-ctx-inlined-func/3}{../../spikes/6.2/inlinedVsGlobalInlined/jspBenchmark.js}

The results for the benchmark are displayed in Figure~\ref{fig:func-key-vs-instance}.
\img{Comparing sending function key in global context against function instance}{../../spikes/6.2/inlinedVsGlobalInlined/result}{fig:func-key-vs-instance}

\note{The improvement shown in Figure~\ref{fig:func-key-vs-instance} will vary if the difference in character length between the key and the function's code does.}

\pagebreak
